\documentclass[a4paper,12pt]{article}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}
\usepackage{tabularx}
\usepackage{enumitem}
\newcolumntype{C}{>{\centering\arraybackslash}X} 
\usepackage{supertabular}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\usepackage{fontawesome5}

%----------------------------------------------------------------------------------------
% JOB ENVIRONMENTS
%----------------------------------------------------------------------------------------
\newenvironment{joblong}[2]
{
\begin{tabularx}{\linewidth}{@{}l X r@{}}
\textbf{#1} & \hfill & #2 \\[3.75pt]
\end{tabularx}
\begin{minipage}[t]{\linewidth}
\begin{itemize}[nosep,after=\strut,leftmargin=1em,itemsep=3pt,label=--]
}
{
\end{itemize}
\end{minipage}
}

%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}
\pagestyle{empty}

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------
\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Siddhant Gahlot} \\[7.5pt]
\href{https://github.com/sid0229}{\raisebox{-0.05\height}\faGithub\ sid0229} \ $|$ \
\href{https://www.linkedin.com/in/siddhant-gahlot/}{\raisebox{-0.05\height}\faLinkedin\ siddhant-gahlot} \ $|$ \
\href{mailto:23f2000839@ds.study.iitm.ac.in}{\raisebox{-0.05\height}\faEnvelope\ 23f2000839@ds.study.iitm.ac.in} \ $|$ \
\href{mailto:gahlotsiddhant@gmail.com}{\raisebox{-0.05\height}\faEnvelope\ gahlotsiddhant@gmail.com} \ $|$ \
\href{tel:+919560358447}{\raisebox{-0.05\height}\faMobile\ +91 95603 58447}
\end{tabularx}

%----------------------------------------------------------------------------------------
%	SUMMARY
%----------------------------------------------------------------------------------------
\section{Summary}
Driven and analytical undergraduate pursuing dual degrees in Artificial Intelligence \& Machine Learning and Data Science. Experienced in data cleaning, visualization, machine learning, and generative AI systems. Proven ability to convert raw data into actionable insights while combining strong technical execution with business understanding through real-world projects.

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE
%----------------------------------------------------------------------------------------
\section{Work Experience}

\begin{joblong}{AI Intern — Prodigal AI (Remote)}{Jul 2025 -- Aug 2025}
\item Worked on Python-based machine learning workflows and AI-driven systems.
\item Applied data preprocessing, feature engineering, and model evaluation techniques.
\item Contributed to real-world AI use cases with a focus on scalability and performance.
\end{joblong}

\begin{joblong}{Generative AI Engineer — Sansoftech Services Pvt. Ltd. (Remote)}{Jun 2025 -- Jul 2025}
\item Developed and integrated generative AI components using prompt engineering techniques.
\item Worked on LLM-powered applications for intelligent automation and user interaction.
\item Collaborated remotely with cross-functional teams to deliver production-ready AI features.
\end{joblong}

%----------------------------------------------------------------------------------------
%	PROJECTS
%----------------------------------------------------------------------------------------
\section{Projects}

\begin{tabularx}{\linewidth}{@{}l r@{}}
\textbf{Citizen Care Pharmacy — Data Analytics for B2C Optimization} & \\[3pt]
\multicolumn{2}{@{}X@{}}{
Analyzed end-to-end pharmacy business data (Greater Noida) to uncover customer trends and operational inefficiencies. Designed analytical dashboards and proposed improvements in inventory planning, pricing strategy, and delivery optimization.
} \\
\end{tabularx}

\vspace{6pt}

\begin{tabularx}{\linewidth}{@{}l r@{}}
\textbf{Finsights — Personal Finance Tracker App} & \\[3pt]
\multicolumn{2}{@{}X@{}}{
Built a full-stack personal finance tracker using HTML, CSS, Python, Node.js, and MongoDB. Developed during the International Upstage API Hackathon to visualize expenses, budgets, and financial insights.
} \\
\end{tabularx}

\vspace{6pt}

\begin{tabularx}{\linewidth}{@{}l r@{}}
\textbf{DeVahan — NFT-Based Vehicle Ownership Platform (Winner — Zenith 4.0)} & \\[3pt]
\multicolumn{2}{@{}X@{}}{
Developed a Web3 platform enabling RTOs to mint vehicle NFTs and users to securely transfer ownership. Implemented MetaMask authentication, IPFS metadata storage, role-based dashboards, and multilingual user interfaces.
} \\
\end{tabularx}

\vspace{6pt}

\begin{tabularx}{\linewidth}{@{}l r@{}}
\textbf{PramaanNFT — Blockchain-Based Property Validation System} & \\[3pt]
\multicolumn{2}{@{}X@{}}{
Designed a smart contract-backed system for minting property NFTs to enable secure and transparent ownership transfer. Integrated PIN-based authentication, dealer/user roles, and AI chatbot support for real-time query handling.
} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\begin{tabularx}{\linewidth}{@{}l X@{}}
2023 -- 2027 & B.Tech in Artificial Intelligence \& Machine Learning, \textbf{University School of Automation and Robotics, GGSIPU (EDC)} \hfill (CGPA: 8.93) \\
2023 -- 2027 & BS in Data Science, \textbf{Indian Institute of Technology, Madras} \hfill (CGPA: 8.21) \\
2022 & Class XII (CBSE, PCM + Economics), DPS Greater Noida \hfill (97.2\%, Top 10 Rank, Medalist) \\
2020 & Class X (ICSE), St. Joseph School, Greater Noida \hfill (95.6\%, Top 5 Rank, Medalist) \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------
\section{Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
Data Analysis \& Visualization & Data Cleaning, Exploratory Data Analysis (EDA), Statistical Modeling, Dashboarding \\
Technical Skills & Python, SQL, Java, Scikit-learn, Pandas, NumPy, Matplotlib, TensorFlow, PyTorch \\
Web \& Cloud Tools & HTML, CSS, React.js, JavaScript, Google Cloud Platform, Microsoft Azure \\
Other & Git, API Integration, Communication, Leadership, Project Management \\
Languages & English (Fluent), Hindi (Fluent) \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	ADDITIONAL INFORMATION
%----------------------------------------------------------------------------------------
\section{Additional Information}
\begin{itemize}[nosep,leftmargin=1em,label=--]
\item Cleared JEE Mains (2023) and CUET (2022)
\item Winner of multiple competitive gaming tournaments
\item Cinematographer for ``Fireworks by Lights Out'' on YouTube
\item Designed and deployed a professional website for a law firm: \href{https://krjlegaloutsource.com}{krjlegaloutsource.com}
\item Certifications: Google Cloud Certified, Microsoft Azure Fundamentals, Machine Learning with Python (Coursera)
\end{itemize}

\vfill
\center{\footnotesize Last updated: \today}

\end{document}
